Self Referencing Sequences

### 2014-10-27 draft.tex
asdasdfasdfasdf
more rule stuff

\begin{theorem}
\label{independentsequences}
If $1<a<b$ then the self-referencing sequence beginning with $a$ generated over $\{1, a, b\}$ and the self-referencing sequence beginning with $b$ generated over $\{1, a, b\}$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

>>>>

\begin{theorem}
\label{independentsequences}
Let $C = \{ 1, a, b\}$ where $1<a<b$. $s(C, a)$ and $s(C, b)$ are independent.
\end{theorem}
\begin{proof}
We proceed by contradiction. If the two sequences are not independent then they must differ by some minimal prefix of length $n$. If we let $a_i$ be the sequence beginning with $a$ and $b_i$ be the sequence beginning with $b$ the
\begin{equation*}
a_{n+k} = b_{k}.
\end{equation*}
We know that the first $b$ terms of the sequence which begins with a $b$ are $b$'s. Because $b>a>1$ no block can be longer then $b$. Thus the terms immediately preceding and following this block in the sequence $a_i$ must not be $b$'s. Because of this the first block of $b_i$ is the $m+1$th block of $a_i$, where $m$ is some positive integer. Since the value of the sequence at position $k$ is also the length of the $k$th block this means that $a_{m+1}=b_1$. In fact the $k$th block of $b_i$ is the $(m+k)$th block of $a_i$ and so 
\begin{equation*}
a_{m+k} = b_k
\end{equation*}

@@

Therefore, we can formulate a set of sufficient conditions to make rules to generate the self-referential sequence with generating set $G$. We want to have a set of rules $R$ where each rule $r \in R$ has length $|r| = l$, such that all $|G|^{l}$ strings are in the rule set and for each $r \in R$
\begin{itemize}
\item each rule reads off the block lengths in the same order of $G$
\item $\sum_{i \in r} i$ is divisible by $l$
\item $l$ is divisible by $|G|$
\end{itemize}
Given these conditions on every rule, we can guarantee that the self-referential sequence is generated. Note that in this case, the above example does not satisfy our rules until we say that $1, 3 \to 3, 1, 1, 1$.

Another exaple, we can have $G = \{ 2, 4 \}$, and we can have that the rules be
\begin{align*}
\text{Rule }A: 2,2 &\to 2, 2, 4, 4 \\
\text{Rule }B: 2,4 &\to 2, 2, 4,4,4,4\\
\text{Rule }C: 4,2 &\to 2,2,2,2,4,4\\
\text{Rule }D: 4,4 &\to 2, 2, 2, 2, 4, 4, 4, 4
\end{align*}
